Time for a rethink: time sub-sampling methods in disparity-through-time analyses

### 2017-12-17 manuscript/time-slice.tex
Abstract ideas

>>>>

Disparity through time analysis are really popular and routinely applied on palaeobiological datasets.

Although many methods exist to measure disparity, all more or less assessed (metrics, tests, etc...), only one method exist for looking at disparity through time: pooling data into time bins.

This may lead to some problems down the line as a methodological bottleneck (i.e. most disparity-through-time analysis are, in the end, based on pooling data into bins).

Here we propose a novel method to complement the disparity-through-time tool-kit: time-slicing.

This method allows to sample disparity through time at any fixed point in time rather than binning data between two fixed points in time.

Additionally, this method allows to use all the phylogenetic data available (tips, nodes \textit{and} branches) and specify the implied model of evolution between each time-slice (punctuated or gradual).

We test this method on four example datasets and compared how it performs at common disparity-through-time analysis: the effect of mass extinction and the time at the maximal and minimal disparity.

We found that the sampling effect has a remarkable effect on our interpretation of disparity-through-time analysis.

Using multiple methods for assessing disparity-through-time (rather than only one!), we can have a better picture of what is happening.
